\documentclass[10pt]{article}
\usepackage[left=1in,top=0.75in,right=1in,bottom=0.5in]{geometry}
%\usepackage[letterpaper, hmargin=1in,vmargin=0.75in]{geometry}
%\usepackage[left=2.5cm,top=3cm,right=2.5cm,bottom=3cm,bindingoffset=0.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts,latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{layout}
%\usepackage{fancyhdr}
%\setlength{\headheight}{15.2pt}
%\pagestyle{fancy}
\def \mbZ {\mathbb{Z}}



\begin{document}

\title{Personal Statement}
\date{}
\author{{\bf Surya Teja Eada} \\  \ \ \\ {\small User ID: teja.suryateja.surya@gmail.com }\\ {\small Applying to the PhD Program } \\ {\small Department of Statistics, University of Connecticut} }
% Check spelling of Connecticut. Also heading? Diversity essay?
\maketitle

\begin{flushright}

{\it Education is the most powerful weapon which you can use to change the world.\\ $-$ Nelson Mandela}


\end{flushright}

At various junctures of my life, I have let the society influence my decisions in a beneficial manner and with these views in mind I hereby do present my "Personal Statement". The biggest characteristic I have imbibed in me from the society is a positive, confident outset to learn and embrace unbiased knowledge through maximum exposure to diversity and an attitude of sharing knowledge. Multiple instances from my life have made me realize that sharing knowledge gives me immense satisfaction. When I was in school pursuing undergraduate studies in Statistics, I enjoyed solving challenging problems and inculcated the habit of discussing them. 
% Correct in previous para Diversity essay

Being a citizen of India which has a vast diversity, I have always found myself amongst people from various cultures and ethnicity in all platforms and phases of my life. I have been in four different states of India for more than a year in each of them, all of them being so different from one another in terms of culture, ideas and social behavior of people. For most part of my life, I lived in a village in southern part of India studying in a school that my parents have established. However, my undergraduate study in the eastern part of India laid foundation stones for me to adapt to other cultures and grow confident with  a positive attitude. The reason for such a boost in confidence have been majorly due to working with diverse individuals (professors, managers, colleagues) during my career.

My parents, being teachers and administrators of a school, have always motivated and inspired me to pursue academics in my life. Both of them being teachers of Mathematics gave me an early head start in the field of Mathematics. This boosted my interest in the subject and kept me ahead of my classmates in solving problems. Interest in Mathematics was also the reason behind choosing Statistics as the field of my undergraduate study. Also the benefits that Indian Statistical Institute (ISI) bestowed upon me, in the form of giving me scholarship, providing excellent professors and researchers in Statistics and applied fields, exposing me to researchers from other prominent universities in the form of guest lectures, providing very good computing facilities and having an extraordinary curriculum in the field of Statistics, has influenced me to consider the idea of pursuing a PhD in Statistics.  Five years of vehement training at ISI has instilled in me all the facets that are required of a graduate student and has guided me in applying for a PhD in your department.

Being affiliated to a few eminent professors, I have been able to appreciate the very basic essence and necessity of research as an integral tool required for the development of mankind and technology. Also, during my latest tenure as a model validator, I could visualize the applications of various statistical techniques and research, in this case particularly, to a bank. Also, the kind of black board discussions that were held at CRISIL with my immediate senior manager have led me to do more research which has ignited in me the interest of doing a PhD.

Today at this juncture of my life I believe that "University of Connecticut" will carve out the path for a more momentous and successful journey. I finally acknowledge my earnest gratefulness for the consideration and sincerely hope to contribute in the field of statistics along with the department of statistics at "University of Connecticut".

%to the reader with the sincere hope that I have been able to portray all the information that was necessary.
 


%\fancyfoot[C] {me}

\begin{flushleft}

Surya Teja Eada.\\
CRISIL Global Research and Analytics, Pune.\\
teja.suryateja.surya@gmail.com

\end{flushleft}


\end{document}