\documentclass[12pt]{article}
\usepackage[left=1in,top = 1in,right=1in,bottom = 1in]{geometry}
%\usepackage[letterpaper, hmargin=1in,vmargin=0.75in]{geometry}
%\usepackage[left=2.5cm,top=3cm,right=2.5cm,bottom=3cm,bindingoffset=0.5cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts,latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{layout}
%\usepackage{fancyhdr}
%\setlength{\headheight}{15.2pt}
%\pagestyle{fancy}
\def \mbZ {\mathbb{Z}}



\begin{document}

\title{Personal Statement}
\date{01/18/2019}
\author{{\bf Surya Teja Eada} \\  {\small Applying to the PhD Program } \\ {\small Department of Statistics, University of Connecticut } }

\maketitle

\begin{flushcenter}

{\it Education is the most powerful weapon which you can use to change the world. $-$ Nelson Mandela}
\\
\end{flushcenter}


Today's world is constantly changing as a result of decisions that are mostly driven by data. Hence, Statistics education is becoming more important than ever and Statisticians are having better opportunities in every field. However to ensure that best Statistical techniques are applied in all fields, Statistics departments need to treat this surge in demand as a responsibility, more than just an opportunity. \\

Steadily, Applied Statistics is becoming a necessary utility, but rigorous Statisticians are few in number. As a consequence, few researchers from other fields and industry employees are sometimes applying quick-learnt threadbare statistical techniques in their quantitative analysis. For example, when I was working in the Finance industry, I observed a practice of fitting Poisson distribution for ``frequency of losses in a year" and stating the reason that it is a standard industry practice. Being the model validator, when I inspected the variable, it had a variance quite larger than the mean. This implied that the model was underestimating its losses and thus the bank was underestimating its capital requirement. I realized how this could jeopardize a whole industry or in this case, even the economy. This motivated me for having a long term career goal to be a researcher who could collaborate with other researchers and map the best statistical practices with various applications in each field. \\

On the other hand, I also intend to be able to teach Statistics and foster next generation Statisticians. I realized that I learn a lot and also get new ideas when I am teaching to friends, colleagues, or students. I think that the task of teaching not only gives me immense satisfaction but also has the ability to boost chances of mapping best statistical practices with various applications as we reiterate various topics of Statistics. \\ 

To accomplish my goals, I will have to learn and apply various Statistical techniques in different fields such as Biology, Finance, Economics, Insurance, Pharmacy, Chemistry etc. Being at University of Connecticut has given me plenty of opportunities to talk to researchers from fields of Statistics, Chemistry, Pharmacy, Computational Biology, Plant Science, Communications, Actuaries and more. This endowed me with an advantage of knowing that Statistics is widely used in all these fields here, and that there are great minds in all the departments of University of Connecticut. On top of it, the faculty in your department has an expertise in application of Statistics in many fields. Thus, I strongly believe that pursuing Ph.D. in your department will allow great collaborations and enhance my chances to fulfil my agendas strategically to meet my goal. \\

Having detailed why pursuing a Ph.D. will benefit me, I also want to let you know what makes me feel confident of having the skills to be an active researcher who can contribute to your department and also the field of Statistics. I've been one of the top 30 candidates chosen ahead of thousands of aspirants at the most prestigious research institute of India in the field of Mathematics and Statistics, Indian Statistical Institute (ISI). \\

Indian Statistical Institute has a rigorous curriculum dedicating five years to teaching many Statistical and Applied Statistics courses.  The institute gives great respect to Statistics by laying very strong foundation with courses in Linear Algebra, Analysis and Probability theory. Advanced topics such as Statistical Inferences, Regression Techniques, Time Series, and Stochastic Processes are discussed in such detail that students are meticulous while applying Statistical techniques in any models. I have personally realized how meticulous I was compared to my peers at applying Statistics during my internships and professional work that spanned for more than three years. \\

During my profession as a Model risk validator, I got to work on projects utilizing parametric and non-parametric statistical techniques such as parameter estimation, hypothesis testing, clustering analysis, logistic regression, Wilcoxon rank sum tests, Markov Models, distribution fitting, and Simulations. Working on these areas in Statistics have kept me constantly engrossed and curious and thus I find applications of these as my areas of interest. Recently, I also started working with Professors Jun Yan and Vladimir Pozdnyakov from department of Statistics, University of Connecticut on parameter estimation in a Stochastic Process that resembles a Hidden Markov Chain. \\

Passion shown on working in the recent Statistics project even while taking courses for my Masters in Applied Financial Mathematics and being a teaching assistant made me feel confident that I can pursue research as a Ph.D. candidate. One thing I have learnt from exposure to industry is to be able to self assess reasonably. When I assessed myself, I found that I have the necessary statistical knowledge and the ability and dedication to take more advanced courses when required to improve my repertoire. I hereby submit my application with the sincerest hope and belief that it will be considered favorably by your department. \\



%\fancyfoot[C] {me}

\begin{flushleft}

Surya Teja Eada,  \\
University of Connecticut. \\

\end{flushleft}


\end{document}