\begin{document}

\title{Diversity Essay - University of Connecticut}
\date{}
\author{{\bf Surya Teja Eada} \\  \ \ \\ {\small User ID: surya.eada@uconn.edu }\\ {\small Applying to the PhD Program } \\ {\small Department of Statistics, University of Connecticut} }
% Check spelling of Connecticut. Also heading? Diversity essay?
\maketitle



 Nelson Mandela said that "Education is the most powerful weapon which you can use to change the world". It is my learning that makes me strongly believe that unrestricted education fuelled by curiosity to explore diversity from around the world, along with ability to share one's knowledge while you learn will go a long way in making the right changes to the already changing world. 
 
 I have been fortunate enough to travel through the vast diversity of my country for my education even when I am young. Though this lead to constant changes and adjustments, I've learnt quickly that this gives me a chance to be exposed to, and to learn from, the vast diversity around me. I believe that everyone has something to contribute to this world and soon this exposure led to me having a positive, confident and calm attitude. 
 
 I gained my exposure to diversity while living in more than 10 different addresses across my country and US, by playing more than 4 sports, by working for a professional job as well as being a teacher, by being socially responsible by bringing plastic awareness and doing charity, by being a multi-lingual movie fan, by being a secretary of a cultural organization at University of Connecticut, by indulging in discussions with PhD students from every other field.
 
 Exposure to diversity at every step in my life made me realize the pool of good and bad choices and helped in my decision. I stayed fit and played sports for university clubs. I've been meticulous but also understanding as a teacher. I learnt to put myself in others shoes before acting. I learnt how I could be more clean, tidy and presentable than what I was. I learnt to tear down borders in my mind, making me more open to treating everyone in this world as the same.
 
It also transformed me from being a small town boy who once had a difficult time conversing even in his native language, to one who now can converse in four languages proficiently. It has transformed me from being a narrow minded kid without the inclination to learn about complicated things going around the world to one who has taken a stance to contribute back to the society and at least have discussions with colleagues regarding the right amendments needed for this world.  Thus I am in constant learning process from exposure to diversity.  
 
On the other hand, being a son of parents who are spending their lives teaching students the right way of life along with other sciences, I always had strong inclination to share my knowledge when necessary. I've become more sure and immensely satisfied when my fellow students, colleagues at work, colleagues in the university, and students thank me and say that I am a good teacher and one who is always friendly. Thus I feel like I am giving back as well. 

Statistics is also a field that has been influential in every other field in today's data driven world. It could be a testing time for the subject, since it is now a utility. There is however a need to think before acting which is a huge learning for me. I feel that in order to utilize Statistics the right way, one needs to have a great plan like a city well planned to allow for its utilization for everyone. Thus there is a huge potential for every statistician.

A quote that has really impressed me is by Margaret Mead when she said that "Never doubt that a small group of thoughtful, committed citizens can change the world. Indeed, it's the only thing that ever has". So, as I am applying to Department of Statistics at the University of Connecticut, I am in hope that my willingness to learn from more diversity and share my diversity can bring ideas to a small group of thoughtful, committed statisticians along with other researchers in University of Connecticut who can one day transform this world to a better one. 





%to the reader with the sincere hope that I have been able to portray all the information that was necessary.
 


%\fancyfoot[C] {me}

\begin{flushleft}

Surya Teja Eada.\\
CRISIL Global Research and Analytics, Pune.\\
teja.suryateja.surya@gmail.com

\end{flushleft}


\end{document}