%-------------------------
% Resume in Latex
% Author : Surya Teja Eada
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Surya Teja Eada} & Email : \href{mailto:surya.eada@uconn.edu}{surya.eada@uconn.edu}\\
   & Mobile : +1-860-208-7249 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Master of Science in Applied Financial Mathematics;  GPA: 4.05}{Aug. 2017 -- Present}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Master of Statistics;  Percent: 62 }{July. 2012 -- May. 2014}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Bachelor of Statistics;  Percent: 62 }{July. 2009 -- May. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Teaching Assistant, Department of Mathematics}{Aug. 2017 - Present}
     
      \resumeItemListStart
      \resumeItem{Research Experience}
        {With the help of my advisor and my course professor who acted as my mentors from the Statistics department, I am working on a project that involves estimation of parameters in a "Brownian Motion driven by Telegraph Process" model. The model is being investigated for applications to Finance like data as they often have stochastic process that changes drift and volatility for different underlying states.}
        
      \resumeItem{Teaching Experience}
        {As a teaching assistant, I held discussion classes for Calculus 2 during the first two semesters, as well as graded homework and quizzes. In the third semester, I was the teaching assistant for an online course, during which I've held 8 hours of in-person office hours and answered student's questions on the online discussion forums in Piazza. During Spring 2019, I am given the role of a primary instructor for Pre-Calculus course.}
        
      \resumeItemListEnd
      
      
    \resumeSubheading
      {CRISIL}{Pune, India}
      {Senior Quantitative Analyst}{July 2014 - May 2017}
      
      \resumeItemListStart
        \resumeItem{Logistic Regression Modeling}
          {As a validator, I have independently modelled Probability of customer's default from Auto New and Auto Used portfolios using logistic regression and further diagnosed the existing model for any inappropriate assumptions and inaccuracies. I also conducted residual diagnostics using various tests and evaluated model's performance using metrics such as Gini's table, KS measure, Somer's D measure.}
          
        \resumeItem{Modeling of Fractional Outcomes}
          {While validating the Wholesale Portfolio's Loss Given Default (LGD) model, I evaluated potential model approaches such as fractional logistic regression, inflated boundary beta distribution, tobit, and Non linear Least Squares (NLS) model based on reviewing "\textbf{Modeling Fractional Outcomes with SAS, Wensui Liu, Jason Xin, 1304-2014}". I have evaluated the performance of each model based on Mean Absolute Error, Variance of Error and inferred that fractional logistic and inflated beta allow were the best approaches for heavy boundary fractional outcomes such as LGD. }
          
        \resumeItem{Distribution Fitting and Monte Carlo Simulations}
          {During validation of an Operation Risk Model, I have independently modelled the number of defaults in a quarter using poisson and negative binomial and loss amount given default using mixture of GPD and log normal distribution and evaluated the loss using 99 percentile of the simulated loss distribution. During this model validation, my contributions were valuable because I have indicated developer's inappropriate use of Poisson (specially single parameter distribution) for distributions with hugely different mean and variance, therefore under-estimating the number of losses corresponding to that particular event type. I have also indicated inappropriate simulation technique being used for obtaining mixture distribution. }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Statistical Knowledge}
      {Parameter Estimation, Hypothesis Testing, Linear Regression, Generalized Linear Regression, ANOVA, Clustering Techniques, Decision Trees.}
    \resumeSubItem{Computer Knowledge}
      {SAS, R, R-Markdown, LATEX, Github, HPC Cluster, MATLAB, Data Structures, SQL, C.}
    \resumeSubItem{Finance and Others}
      {Micro Economics, Finance Modeling of Risk, Actuarial Modeling, CAPM model, Interest rate models, Black-Scholes Option pricing model}
    \resumeSubItem{Social Skills}
      {Profecient at Communication, University of Connecticut's Badminton Club team member, Secretary of Tarang (Student Orgranization) at UConn, Sports Committee secretary at ISI, CRISIL's voluntary organization \textit{Plastic Awareness for Environment and Society} (PAES) member}      
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
