\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Surya Teja Eada} & Email : \href{mailto:surya.eada@uconn.edu}{surya.eada@uconn.edu}\\
Department of Statistics   & Mobile : +1 (860) 771-8215 \\
University of Connecticut & \href{https://github.com/suryaeada9}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {suryaeada9}} \\
& \href{https://www.linkedin.com/in/suryaeada9}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {Surya Teja Eada}}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Ph.D. in Statistics; GPA: 4.09}{Aug. 2019 -- Present} \\ 
      \begin{itemize}
      \item \textbf{Dissertation}: ``Brownian and Meixner Processes
      driven by Telegraph Process": My research is primarily focused
      on Brownian and other Levy Processes governed by two states of
      the telegraphers process. The core aim of this research is to
      advance the field of parameter estimation, especially in
      scenarios where only spatial increments are observed. This has
      applications to Finance and animal movement. A Paper related to
      Brownian process driven by Telegraph is currently under review
      for journal publication.
      \end{itemize}
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Master of Science in Applied Financial Mathematics;  GPA: 4.05}{Aug. 2017 -- May. 2019}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Master of Statistics;  Percentage: 62 }{July. 2012 -- May. 2014}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Bachelor of Statistics;  Percentage: 62 }{July. 2009 -- May. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CRISIL}{Pune, India}
      {Senior Quantitative Analyst}{July 2014 - May 2017}
      \begin{itemize}
        \item \textbf{Credit Risk Modeling}:
        \begin{itemize}
            \item  Outsourcing consultant for a US commercial bank,
        specialized in model validation working for Comprehensive
        Capital Analysis and Review (CCAR) stress testing models.
            \item Validated logistic regression models utilized for Probability
        of Default and fractional outcome regression models for Loss
        Given Default in HELOC and Auto loans. 
            \item Validated wholesale credit risk models that utilize S\&P ratings.
            \item Helped in responding to questions on validation
            during federal audit and also excelled in a mentoring role.
        \end{itemize}\vspace{-5pt}
        
        \item \textbf{Operation Risk Models, House pricing models}: 
        \begin{itemize}
            \item Detected inappropriate use of Poisson distribution,
            preventing underestimation of operational loss values for
            specific events.
            \item Offered feedback in the inaccurate use of type of
            testing (Wilcoxon test instead of Wilcoxon signed rank
            test) that cut client spending, resulting in cost-saving.
            \item Received certificates of appreciation for significant model validation contributions.
        \end{itemize}\vspace{-5pt}
      
    \end{itemize}

    \resumeSubheading
    {University of Connecticut}{Storrs, CT}
    {Teaching Assistant, Dept. of Statistics and Dept. of Mathematics}{Aug. 2017 - Present}
      \begin{itemize}
          \item Accumulated a wealth of teaching experience over 12 semesters.
          \item Held diverse roles including leading discussions,
          instructing a complete online course, and serving as the primary instructor for various courses.
          \item Taught across different levels within both statistics and mathematics departments.
      \end{itemize}

    \vspace{-1pt}\item
      \textbf{Internship}
    \begin{itemize}
        \item \textbf{Institute for Mathematical and Statistical
        Innovation (IMSI), Storrs, CT, Summer 2021} \textbf{Leaf Area
        and Yield Model}: Utilized a partitioning logistic module to
        study sorghum, evaluating yield by leaf weight per unit area.
        Determined actual yields and areas for optimal model
        parameters, comparing model predictions with real-world data.
        Explored various loss definitions, ultimately adopting a
        normed Mahalanobis loss to optimize parameters in the module. 
            
        \item \textbf{Traveler's, Hartford, CT, Spring 2019}: Collaborated on a
        semester-long experiential project to assess the impact of
        modern technology and direct-to-consumer channels on Traveler's
        primary distribution method, the "Independent Agency channel"
        and provide recommendations. 
        \item \textbf{Deloitte U.S. India Ltd., Hyderabad, India,
        Summer 2013}:
        Derived rules from the CHAID decision tree analysis to
        efficiently create appropriate customer segments for selling
        specific electronic products and rules to enhance cross-sale
        opportunities.
        \item \textbf{eClerx, Mumbai, India, Summer 2012}: Developed training decks on linear regression and cluster analysis for onboarding new employees. 
    \end{itemize}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section*{Other Projects}

\begin{itemize}

\item \textbf{Travelers Fraud Detection, Fall 2021}
    \begin{itemize}
        \item Implemented machine learning models including XGBoost, Ridge Classification, and Logistic Regression to detect fraudulent insurance claims.
        \item Surpassed the benchmark F1 score (considered as metric),
        presented the findings.
    \end{itemize}\vspace{-5pt}

\item \textbf{Binomial Observations from Multinomial}
    \begin{itemize}
        \item Estimated likelihoods of binomial outcomes within a multinomial framework.
        \item Determined the required sample size to ensure precision within confidence intervals.
    \end{itemize}\vspace{-5pt}
\end{itemize}\vspace{-5pt}

\section*{Presentations}

\begin{itemize}
    \item Delivered an invited talk on ``Brownian Processes driven by
    Telegrapher's process'' at the New England Statistical Symposium (NESS) 2023.
    \item Delivered a workshop ``Introduction to Python'' at
    University of Connecticut Sports Analytics Symposium (UCSAS) 2021.
\end{itemize}

\section*{Publications}
Eada, S. T., Pozdnyakov, V., \& Yan, J. (2023). Discretely
Observed Brownian Motion Goverened by Telegrapher's Process:
Estimation and Applications to Finance (under review).

\section*{Skills}
    \begin{itemize}
        \item \textbf{Areas of Interest}: Time Series, Parameter Estimation, Hypothesis Testing, Regression \& ANOVA analysis, Clustering and Classification
        \item \textbf{Technology}: R, Python, SAS, Markdown, Tex,
        Github, HPC Cluster, SQL
        \item \textbf{Finance}: Risk Modeling, Actuarial Models, CAPM model, yield curve modeling, Black-Scholes model
    \end{itemize}     

\section*{Awards}

\begin{itemize}
    \item H. Fairfield Smith and Dolores S. Smith Award for
    Excellence in Applied Statistics (2020)  
    \item Certificate of Excellence for the Best Performance in
    Probability (2021)
    \item INSPIRE Scholarship for graduate students with outstanding
    ability (2009-2014)
    \item Won Individual Bright Spark Quarterly Award (Q1 2015),
    Executive Excellence Quarterly Team Award (Q2 2015), Monthly CLAP
    Awards (November, December 2015), Service Excellence Quarterly
    Award (Q4 2015), Analytical Excellence Quarterly Award (Q2 2016)
    at CRISIL.
\end{itemize}  
%-------------------------------------------
\end{document}