\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Surya Teja Eada} & Email : \href{mailto:surya.eada@uconn.edu}{surya.eada@uconn.edu}\\
Department of Statistics   & Mobile : +1 (860) 771-8215 \\
University of Connecticut & \href{https://github.com/suryaeada9}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {suryaeada9}} \\
& \href{https://www.linkedin.com/in/suryaeada9}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {Surya Teja Eada}}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Ph.D. in Statistics;  GPA: 4.09}{Aug. 2019 -- Present}
       \resumeItemListStart
      \resumeItem{Continuous Stochastic Processes driven by Telegraph Process}
    {My research is primarily focused on Brownian and other Levy
    Processes, specifically those governed by two states of the
    telegraphers process. The core aim of this research is to advance
    the field of parameter estimation, especially in scenarios where
    only spatial increments are observed. This has applications to
    Finance and ecology. Papers related to this research is currently
    under review for journal publication.}
         \resumeItemListEnd
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Master of Science in Applied Financial Mathematics;  GPA: 4.05}{Aug. 2017 -- May. 2019}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Master of Statistics;  Percentage: 62 }{July. 2012 -- May. 2014}
    \resumeSubheading
      {Indian Statistical Institute}{Kolkata, India}
      {Bachelor of Statistics;  Percentage: 62 }{July. 2009 -- May. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT}
      {Ph.D.  student and Teaching Assistant, Dept. of Statistics and Dept. of Mathematics}{Aug. 2017 - Present}
        \resumeItemListStart        
      \resumeItem{Teaching Experience}
        {In parallel to my research, I have accumulated a wealth of teaching experience throughout my academic journey, spanning 12 semesters. These teaching roles have been diverse, including responsibilities as a discussion leader, an online course teaching assistant, and as the primary instructor for multiple courses within the statistics and mathematics departments. }        
      \resumeItemListEnd
            
    \resumeSubheading
      {CRISIL}{Pune, India}
      {Senior Quantitative Analyst}{July 2014 - May 2017}
      
      \resumeItemListStart
        \resumeItem{Model Validation}
          {In my role as an outsourcing consultant for a US commercial bank, my primary responsibility involved model validation, a key pillar in model risk management. This involves independently developing code for key projects including customer default predictions, calculating Loss Given Default, and operational risk models based on simulations. These tasks require a deep understanding of financial principles and advanced statistical methods, ensuring that models are accurate, since they are supposed to meet stringent regulatory and internal standards. Beyond these technical duties, I played a mentor role, guiding and assisting others in the team.}
          
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Internships}
      {2 months at Institute for Mathematical and Statistical Innovation (IMSI), 2 months at Deloitte U.S. India Ltd.  (Advanced Analytics team),  2 months at eClerx, semester for Traveler's through UConn ELC.}
    \resumeSubItem{Statistics Areas of Interest}
      {Time Series, Parameter Estimation, Hypothesis Testing, Regression \& ANOVA analysis, Clustering and Classification problems.}
    \resumeSubItem{Technology}
      {R, Python, SAS, Markdown, Tex, Github, HPC Cluster.}
    \resumeSubItem{Finance and Others}
      {Risk Modeling, Actuarial Models, CAPM model, yield curve modeling, Black-Scholes model}
    \resumeSubItem{Social}
      {Badminton Club member, Graduate Statistics Committee member,  Secretary and President of Tarang (Student Orgranization) at UConn,  member at CRISIL's voluntary activity {\bf Plastic Awareness for Environment and Society}}      
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
